Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-04-30 files/Chapter2/generalvibrationmodel.tex
Chapter 2.4.2 and 4.2

\section{Modal analysis}\label{sec:existence:ModalAnalysis}
\subsection{Timoshenko beam}\label{subsec:Timoshenko_Modal_Analsis}
To understand what is meant by modal analysis, it is in the first place necessary to consider modes of vibration. And to understand how modal analysis is applied, a Timoshenko beam is used as an example. Specifically, Problem T-1 as it is easy to illustrate the idea of modal analysis.

@@

Solutions to Problem T-1E is a pair of functions $\langle \tilde{w}, \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$. Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are possible solutions of the differential equations and satisfy the boundary conditions.

Due to this periodicity of these solutions for the eigenvalue problem Problem T-1E, it has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$. The vector $\langle 0, 1 \rangle$ also satisfies the eigenvalue problem with boundary conditions. This solution is called the constant solution.

A systematic approach to obtain the eigenvalues and eigenfunctions is given in \cite{VV06}. This is discussed in in Section 4.2. From \cite{VV06}, the following theorem can be derived and confirms the validity of our trial solutions for the eigenvalue problem.

@@

@@

\subsection{General vibration problem new}
This section is a discussion of a general vibration problem. The discussion will refer to the article \cite{CVV18}. Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. The authors of \cite{CVV18} do take damping into consideration, which is not covered in this dissertation. Assume there is no damping and no forcing.

@@

Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions:
\begin{flalign}
	T_n(t) &=  A_n \cos(\omega_n t) + B_n \sin(\omega_n t) \quad \textrm{ if } \lambda > 0, \label{lambda_1}\\
	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda = 0, \label{lambda_2}\\
	T_n(t) &=  A_n \cosh(\mu_n t) + B_n \sinh(\mu_n t) \quad \textrm{ if } \lambda < 0. \label{lambda_3}
\end{flalign}

>>>>

\section{Modal analysis}\label{sec:existence:ModalAnalysis}
\subsection{Timoshenko beam}\label{subsec:Timoshenko_Modal_Analsis}
To understand what is meant by modal analysis, it is in the first place necessary to consider modes of vibration. And to understand how modal analysis is applied, a Timoshenko beam is used as an example. Specifically, Problem T-1 as the boundary conditions makes it easy to illustrate the idea of modal analysis. A systematic approach to modal analysis for the Timoshenko beam theory is discussed in Chapter 4.

@@

Solutions to Problem T-1E is a pair of functions $\langle \tilde{w}, \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$. Substitution  that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are possible solutions of the differential equations and satisfy the boundary conditions.

Due to the periodicity of these solutions, the eigenvalue problem has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$. Another solution is the vector $\langle 0, 1 \rangle$ which also satisfies the eigenvalue problem with boundary conditions. This solution is called the constant solution.

A systematic approach to obtain the eigenvalues and eigenfunctions is given in \cite{VV06}. This is discussed in more detail in Section \ref{sec:Timo:EigenvalueProblem}. To verify the trial solutions for Problem T-1E, the following theorem can be derived from \cite{VV06}.

@@

\begin{proof}
	See Section 4.2.
\end{proof}

@@

\subsection{General vibration problem new}
This section is a discussion of a general vibration problem. The discussion will refer to the article \cite{CVV18}. In this article, the authors take damping into consideration, which is not covered in this dissertation. Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. Assume there is no damping and no forcing.

@@

Since this differential equation is a simple second order differential equation, T(t) has the following possible solutions:
\begin{flalign}
	T_n(t) &=  A_n \cos(\sqrt{\lambda_n} t) + B_n \sin(\sqrt{\lambda_n} t) \quad \textrm{ if } \lambda > 0, \label{lambda_1}\\
	T_n(t) &=  A_n + B_n t \quad \textrm{ if } \lambda = 0, \label{lambda_2}\\
	T_n(t) &=  A_n \cosh(\sqrt{-\lambda_n} t) + B_n \sinh(\sqrt{-\lambda_n} t) \quad \textrm{ if } \lambda < 0. \label{lambda_3}
\end{flalign}
